\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-23 doc/paper.Rmd
results from hamby-44

\begin{table}[ht]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{rrrlrrl}
  \hline
  & \multicolumn{3}{l}{\bf CS1} & \multicolumn{3}{l}{\bf CS2} \\
$w_o$ & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) \\ 
  \hline
90 & 0.068 & 0.330 & 0.850 (0.835, 0.865) & 0.075 & 0.242 & 0.877 (0.863, 0.890) \\ 
  120 & 0.065 & 0.309 & 0.864 (0.850, 0.878) & 0.072 & 0.236 & 0.890 (0.877, 0.903) \\ 
  130 & 0.065 & 0.317 & 0.863 (0.850, 0.877) & 0.072 & 0.224 & 0.898 (0.886, 0.910) \\ 
  140 & 0.065 & 0.304 & 0.873 (0.859, 0.886) & 0.071 & 0.229 & 0.902 (0.891, 0.914) \\ 
  150 & 0.067 & 0.326 & 0.863 (0.850, 0.877) & 0.072 & 0.225 & 0.904 (0.892, 0.916) \\ 
  180 & 0.061 & 0.326 & 0.877 (0.864, 0.890) & 0.070 & 0.229 & 0.907 (0.896, 0.919) \\ 
  210 & 0.064 & 0.342 & 0.865 (0.851, 0.878) & 0.066 & 0.231 & 0.906 (0.895, 0.918) \\ 
   \hline
\end{tabular}
\end{adjustbox}
\caption{\label{tab:aucs} Overview of results as shown in Figures \ref{fig:roc} and \ref{fig:eer}. FPR is the observed rate of false positives (for a fixed level $\alpha = 0.05$) or type I error rate, FNR is the false negative rate or type II eror rate. Area under the curve (AUC) is shown with confidence intervals. }
\end{table}

@@

```{r h44, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="AUC and EER for methods CS1 and CS@ based on high resolution scans of Hamby 44. "}
if (!file.exists("../data/h44.rds")) {
files <- dir("../data/hamby44/", pattern="rds", recursive=TRUE)

h44 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/hamby44", file))
  tmp$source <- file
  tmp <- tmp %>% mutate(
    match = replace(match, is.na(match), FALSE)
  )
  h44 <- rbind(h44, tmp)
}
  saveRDS(h44, "../data/h44.rds")
} else {
  readRDS("../data/h44.rds")
}

>>>>

\begin{table}[hbtp]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{rrrlrrl}
  \hline
  & \multicolumn{3}{l}{\bf CS1} & \multicolumn{3}{l}{\bf CS2} \\
$w_o$ & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) \\ 
  \hline
90 & 0.068 & 0.330 & 0.850 (0.835, 0.865) & 0.075 & 0.242 & 0.877 (0.863, 0.890) \\ 
  120 & 0.065 & 0.309 & 0.864 (0.850, 0.878) & 0.072 & 0.236 & 0.890 (0.877, 0.903) \\ 
  130 & 0.065 & 0.317 & 0.863 (0.850, 0.877) & 0.072 & 0.224 & 0.898 (0.886, 0.910) \\ 
  140 & 0.065 & 0.304 & 0.873 (0.859, 0.886) & 0.071 & 0.229 & 0.902 (0.891, 0.914) \\ 
  150 & 0.067 & 0.326 & 0.863 (0.850, 0.877) & 0.072 & 0.225 & 0.904 (0.892, 0.916) \\ 
  180 & 0.061 & 0.326 & 0.877 (0.864, 0.890) & 0.070 & 0.229 & 0.907 (0.896, 0.919) \\ 
  210 & 0.064 & 0.342 & 0.865 (0.851, 0.878) & 0.066 & 0.231 & 0.906 (0.895, 0.918) \\ 
   \hline
\end{tabular}
\end{adjustbox}
\caption{\label{tab:aucs} Overview of results as shown in Figures \ref{fig:roc} and \ref{fig:eer}. FPR is the observed rate of false positives (for a fixed level $\alpha = 0.05$) or type I error rate, FNR is the false negative rate or type II eror rate. Area under the curve (AUC) is shown with confidence intervals. }
\end{table}

@@

The high-resolution scans of Hamby set 44 are capturing images at a resolution of $0.645 \mu m$ per pixel. On average, land engraved areas are 3000 pixels in length. A coarseness of $c = 0.15$ was found to be sufficient in removing any bullet curvature.
\autoref{fig:h44} shows the resulting EER and AUC for methods CS1 and CS2 based on two sizes of validation windows ($w_v \in 75, 125$) and optimization window sizes around 300 pixels (10 percent of the average length). Interestingly, the overall performance of both CS1 and CS2 is a lot lower for the high resolution version of Hamby-44 than for the lower resolution scans. The area under the curve overall is significantly lower for the high resolution scans than for the previous set of scans. Partly, this might be due to the particular choice of the parameters.

```{r h44, fig.width=7.75, fig.height=5, out.width='\\textwidth', fig.cap="AUC and EER for methods CS1 and CS2 based on high resolution scans of Hamby 44. "}
if (!file.exists("../data/h44.rds")) {
files <- dir("../data/hamby44/", pattern="rds", recursive=TRUE)

h44 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/hamby44", file))
  tmp$source <- file
  tmp <- tmp %>% mutate(
    match = replace(match, is.na(match), FALSE)
  )
  h44 <- rbind(h44, tmp)
}
  saveRDS(h44, "../data/h44.rds")
} else {
  h44 <- readRDS("../data/h44.rds")
}

### 2018-05-23 doc/paper.tex
results from hamby-44

\autoref{fig:type1} shows observed type I error rates across a range of
optimization windows \(w_o\). Generally, observed type I errors are
higher than expected. Method CS1 shows in this instance slightly better
performance than method CS2, but for both an increase in the size of the
optimization window leads to a decrease in the observed type I error
rates.

@@

>>>>

\autoref{fig:type1} shows observed type I error rates (FPR) across a
range of optimization windows \(w_o\). Generally, observed type I errors
are higher than expected. Method CS1 shows in this instance slightly
better performance than method CS2, but for both an increase in the size
of the optimization window leads to a decrease in the observed type I
error rates.

@@

\hypertarget{high-resolution-hamby-44-scans}{%
\subsection{High resolution Hamby 44
scans}\label{high-resolution-hamby-44-scans}}

The high-resolution scans of Hamby set 44 are capturing images at a
resolution of \(0.645 \mu m\) per pixel. On average, land engraved areas
are 3000 pixels in length. A coarseness of \(c = 0.15\) was found to be
sufficient in removing any bullet curvature. \autoref{fig:h44} shows the
resulting EER and AUC for methods CS1 and CS2 based on two sizes of
validation windows (\(w_v \in 75, 125\)) and optimization window sizes
around 300 pixels (10 percent of the average length). Interestingly, the
overall performance of both CS1 and CS2 is a lot lower for the high
resolution version of Hamby-44 than for the lower resolution scans. The
area under the curve overall is significantly lower for the high
resolution scans than for the previous set of scans. Partly, this might
be due to the particular choice of the parameters.

{\centering \includegraphics[width=\textwidth]{figures/h44-1}

\caption{AUC and EER for methods CS1 and CS2 based on high resolution scans of Hamby 44. }\label{fig:h44}
\end{figure}
